---
title: "R Project 1 - Hello R"
author: "Steven Swenson"
date: "Due Fed 3rd"
output: 
  html_document: 
    highlight: kate
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

Per the help file 
The datasaurus data frame has 
  
  * 1846 rows and 3 columns
  * Variables include:
     + dataset name
     + x
     + y 
  
  

### Exercise 2

Checking the dataset with a frequency chart. Interestingly we find that there are thirteen datasets in this collection instead of the 12 we might expect from the name.

```{r}
datasaurus_dozen%>%
  count(dataset)%>%
  print(13)
```

Now let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=5}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Plotting the data in the "star" dataset from the dinosaurus_dozen



```{r plot-star, fig.height=3.5, fig.width=3.5}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

#### Correlation between x and y in star dataset 
 
```{r cor-star}

dino_data %>%
  summarize(r = cor(x, y))

```

### Exercise 4

Loading the "Circle" data set and plotting it

```{r fig.height=3, fig.width=3}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()

```


Calculating the linear correlation for the "circle" data 
```{r cor-circle}
dino_data %>%
  summarize(r = cor(x, y))


```

### Exercise 5


Using faceting we can plot all of the datasets in the datasaurus data at once.

```{r fig.height=6, fig.width=6 }

ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
geom_point()+
facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols
theme(legend.position = "none")
```
And now we can use the group_by function to generate all the summary correlation coefficients as well.

```{r cor-groups}
datasaurus_dozen %>%
group_by(dataset) %>%
summarize(r = cor(x, y)) %>%
print(13)
```
